The Mysterious Lives Of Speckles. I. Residual atmospheric speckle lifetimes in ground-based coronagraphs

### 2021-05-26 specklelives.tex
Updates from Overleaf

\section{The Potential of \textbf{PSF} Reconstruction Post-Processing}
\label{sec:reconstruction}
\textbf{The reconstruction of the post-AO PSF using AO system telemetry has been studied for some time, primarily focused on the long-exposure PSF, e.g. \citet{1997JOSAA..14.3057V} and see the recent review by \citep{2020SPIE11448E..0AB}.  PSF reconstruction in the context of high-contrast imaging is typically based on image data alone \citep{2006ApJ...641..556M,2007ApJ...660..770L,2012ApJ...755L..28S}, however the potential for telemetry-based PSF estimation in high-contrast imaging has been recognized \citep{2013ApJ...767...21F,2013ApJ...767..100C}. Here we use our treatment of the intensity dynamics behind an AO-fed coronagraph to analyze the performance of PSF estimation and subtraction.  We are particularly motivated by the use of WFS telemetry to improve on the sensitivity limit set by atmospheric speckle lifetimes, however this analysis could be applied to conventional post-processing such as the KLIP algorithm \citep{2012ApJ...755L..28S}.}

@@

In Section \ref{sec:psd_lifetime} we developed the expansion of the intensity time-series in terms of orthonormal Legendre polynomials $P_\eta$.  \textbf{For a segment of the reconstructed intensity of length T, we measure the coefficients of the Legendre polynomials}
\begin{equation}
\hat{a}_\eta = \int_{-1}^1 \hat{I}_{mn}(\frac{T}{2}\xi) P_\eta(\xi) d\xi. 
\end{equation}
\textbf{We then subtract the first $N$ Legendre modes of the reconstructed time-series from the measured focal plane intensity time-series, giving the ``post-processed'' intensity} 
\begin{equation}
I_{mn,pp}(t) = I_{mn}(t) - \sum_{\eta=0}^{\eta=N-1} \hat{a}_\eta P_\eta\left(\frac{2}{T}t\right). 
\end{equation}
\textbf{The outcome of this post-processing} will be fewer long-term correlations as the low order modes are successively subtracted, which will in turn lower the speckle lifetime.  We can describe this outcome statistically as a high-pass filter (HPF).  The PSD of a mode is
\begin{equation}
\mathcal{T}_\eta(f) = \mathcal{T}(f) \left|Q_\eta(f)\right|^2
\end{equation}
where ${Q}_\eta$ is the Fourier transform of $P_\eta$, which we derive in Appendix \ref{app:tau_psd}, giving
\begin{equation}
 \left|Q_\eta(f)\right|^2 = \left(\frac{2\eta+1}{2}\right)\frac{J_{\eta+\frac{1}{2}}^2(\pi T f)}{T f}.
\end{equation}
After fitting and subtracting $N$ modes, the speckle intensity PSD will be high-pass filtered with squared transfer function
\begin{equation}
\left| H_\mathrm{HPF}(f;N) \right| ^2 = 1 - \frac{1}{2}\sum_{\eta=0}^{\eta=N-1} (2\eta+1) \frac{J_{\eta+\frac{1}{2}}^2(\pi T f)}{T f}.
\end{equation}
We show examples of the transfer functions for this filter in Figure \ref{fig:leghpf}.

>>>>

\section{The Potential of \textbf{PSF} Reconstruction Post-Processing}
\label{sec:reconstruction}
\textbf{The reconstruction of the post-AO PSF using AO system telemetry has been studied for some time, primarily focused on the long-exposure PSF, e.g. \citet{1997JOSAA..14.3057V} and see the recent review by \citet{2020SPIE11448E..0AB}.  PSF reconstruction in the context of high-contrast imaging is typically based on image data alone \citep{2006ApJ...641..556M,2007ApJ...660..770L}, however the potential for telemetry-based PSF estimation in high-contrast imaging has been recognized \citep{2013ApJ...767...21F,2013ApJ...767..100C}. Here we use our treatment of the intensity dynamics behind an AO-fed coronagraph to analyze the performance of PSF estimation and subtraction.  We are particularly motivated by the use of WFS telemetry to improve on the sensitivity limit set by atmospheric speckle lifetimes, however this analysis could be applied to conventional post-processing such as the KLIP algorithm \citep{2012ApJ...755L..28S}.}

@@

In Section \ref{sec:psd_lifetime} we developed the expansion of the intensity time-series in terms of orthonormal Legendre polynomials $P_\eta$.  \textbf{For a segment of the reconstructed intensity of length T, we measure the coefficients of the Legendre polynomials}
\begin{equation}
\hat{a}_\eta = \int_{-1}^1 \hat{I}_{mn}\left(\frac{T}{2}\xi\right) P_\eta(\xi) d\xi. 
\end{equation}
\textbf{We then subtract the first $N$ Legendre modes of the reconstructed time-series from the measured focal plane intensity time-series, giving the ``post-processed'' intensity} 
\begin{equation}
I_{mn,pp}(t) = I_{mn}(t) - \sum_{\eta=0}^{\eta=N-1} \hat{a}_\eta P_\eta\left(\frac{2}{T}t\right). 
\end{equation}
\textbf{The outcome of this post-processing} will be fewer long-term correlations as the low order modes are successively subtracted, which will in turn lower the speckle lifetime.  We can describe this outcome statistically as a high-pass filter (HPF).  The PSD of a mode is
\begin{equation}
\mathcal{T}_\eta(f) = \mathcal{T}(f) \left|Q_\eta(f)\right|^2
\end{equation}
where ${Q}_\eta$ is the Fourier transform of $P_\eta$, which we derive in Appendix \ref{app:tau_psd}, giving
\begin{equation}
 \left|Q_\eta(f)\right|^2 = \left(\frac{2\eta+1}{2}\right)\frac{J_{\eta+\frac{1}{2}}^2(\pi T f)}{T f}.
\end{equation}
After fitting and subtracting $N$ modes, the speckle intensity PSD will be high-pass filtered with squared transfer function
\begin{equation}
\left| H_\mathrm{HPF}(f;N) \right| ^2 = 1 - \frac{1}{2}\sum_{\eta=0}^{\eta=N-1} (2\eta+1) \frac{J_{\eta+\frac{1}{2}}^2(\pi T f)}{T f}.
\end{equation}
We show examples of the transfer functions for this filter in Figure \ref{fig:leghpf}.
